### 2021-01-28 docs/manuscript.tex
notizen zu face-to-face meeting

\subsection{A real-world example}

@@

Fisher's exact test and  HAMdetector were applied to the same data (table~\ref{tab:false-positives}).
The posterior probabilities given by HAmdetector denote the probability that the corresponding regression coefficient is positive. Associations with strong support in our model have a posterior probability close to 1, associations with no support a probability close to 0.5 (corresponding to a regression coefficient centered around 0).

@@

>>>>

\subsection{Generalization}
no overfitting but improvements show for different data sets and different viruses
supplementary figures

\subsection{A real-world application}

@@

Fisher's exact test and HAMdetector were applied to the same data (table~\ref{tab:false-positives}).
The posterior probabilities given by HAMdetector denote the probability that the corresponding regression coefficient is positive. Associations with strong support in our model have a posterior probability close to 1, associations with no support a probability close to 0.5 (corresponding to a regression coefficient centered around 0).

@@

if quality is the same for all viruses: differences between immune/virus interactions become visible

recombinant forms

4-digit partial pooling
